Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}

### 2024-01-04 src/tex/ms.tex
[showyourwork] overleaf sync

For the study in this paper, we use all the publicly available data from the \ac{harps} and the ESO 3.6m telescope in Chile.
%
In addition, we complement this with observations with the \ac{UVES} at the Very Large Telescope in Chile.

@@

To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
%
The details for these observations are given in \cite{vansluijs2019}, and summarised here.
%
These observations were all obtained using the same instrument setup.
%
We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
%
In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim$3730 $\AA$  to $\sim$5000 $\AA$ in the blue arm, and $\sim$5650 $\AA$ to $\sim$9560 $\AA$ in the red arm.
%
For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
%
For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).

The data were reduced using the ESO \ac{UVES} pipeline version \textcolor{red}{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible. The flat-field was applied on a pixel-by-pixel basis.\textcolor{red}{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region. Optimal extraction was performed, using an empirical profile}

@@

We have theoretical specrtra of CN shown in Figure~\ref{fig:CN_theory}.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/ccf_mean.pdf}
        \caption{Cross correlation for different number densities of CN averaged over many spectra.}
        \label{fig:ccf}
        \script{plot_ccf_mean.py}
    \end{centering}
\end{figure}

>>>>

For the study in this paper, we use all the publicly available data from the \ac{harps} and the ESO 3.6m telescope in Chile.
%
In addition, we complement this with observations with the \ac{uves} at the Very Large Telescope in Chile.

@@

To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
%
The details for these observations are given in \cite{vansluijs2019}, and summarised here.
%
These observations were all obtained using the same instrument setup.
%
We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
%
In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA to $\sim 5000$ \AA in the blue arm, and $\sim 5650$ \AA to $\sim 9560$ \AA in the red arm.
%
For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
%
For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).

The data were reduced using the ESO \ac{uves} pipeline version \textcolor{red}{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible. The flat-field was applied on a pixel-by-pixel basis.\textcolor{red}{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region. Optimal extraction was performed, using an empirical profile}

@@

We have theoretical spectra of CN shown in Figure~\ref{fig:CN_theory}.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/ccf_mean.pdf}
        \caption{Cross correlation for different number densities of CN averaged over many spectra.}
        \label{fig:ccf_mean}
        \script{plot_ccf_mean.py}
    \end{centering}
\end{figure}
